Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-20 Response/Response 3/response-3.tex

\reviewF{The authors have modified the manuscript taken into account the reviewers' comments. However, the proof of convergence still lacks of convincing argumentation to make this paper suitable for publication. Two main aspects are arguable as follows: }

\vspace{1eM}
\underline{\textbf{Response:}} We thank the reviewer for pointing out the mistake in our previous convergence proof. Based on the reviewer's comments and suggestions, we have rewritten Appendix A-D using subsequence convergence instead of claiming the sequence convergence. We hope that our current changes will be convincing enough to make the convergence proof complete.

%As an observation, we have noted that the feasible set of nonconvex problem (16) need not be bounded, even if the feasible set of the original nonconvex problem in (6) and the relaxed \ac{MSE} reformulated problem in (26) is bounded. It happens in problem (16) because of the newly introduced optimization variables in (16b) and (16c) to relax the \ac{SINR} expression, since \eqn{\beta_{l,k,n}} can assume any value satisfying (16c) without violating any other constraints in (16) when \eqn{\gamma_{l,k,n} = 0}. Therefore, to ensure boundedness of the feasible set of problem (16), we can include an additional bounding constraint on \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}}, where \eqn{B_{\max}} can be a maximum interference threshold seen by any user in the network for a given maximum transmit power budget \eqn{P_{\max}}. Note that the additional constraint on \eqn{\beta_{l,k,n}} will not alter the solution space of other optimization variables. However, as a consequence of considering the regularized objective in (46b), the additional constraint on \eqn{\beta_{l,k,n}} is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in (46b). We have highlighted this discussion on page 6, after (28).

\begin{enumerate}

@@

	\item \reviewF{When discussing the convergence of the \ac{SCA} algorithm (Appendix A-C), the authors claim that the \ac{SCA} algorithm converges because the objective function is strictly decreasing and the minimizer in each iteration is unique. However, this is in general not enough to guarantee the convergence of the whole sequence. Instead, one can only claim that every limit point of the whole sequence is a stationary point, or globally optimal solution if the problem is convex. As an example, simply consider the gradient projection algorithm, where each subproblem is strongly convex and the objective function  is strictly decreasing but the whole sequence may not converge. The authors are referred to Bertsekas'  book: Nonlinear Programming.}

	\vspace{1eM}
	\underline{\textbf{Response:}} We thank the reviewer for pointing out that the sequence of iterates generated by the \ac{SCA} algorithm in each \ac{AO} step need not be convergent in Appendix A-C. Based on the reviewer's reference to Nonlinear Programming textbook, we have realized that our earlier convergence proof is not mathematically rigorous. We apologize for our emphasis on the convergence of iterates in our previous manuscript. As suggested by the reviewer, stationarity of limit points of the whole sequence of iterates is now addressed in Appendix A-D by using the following statements. 
	\begin{itemize}
		\item The sequence of iterates generated by the algorithm is bounded, therefore, we can only claim that there exist at least one subsequence that converges to a limit point of the original sequence.
		\item Using a convergent subsequence, we then discuss that every limit point is a stationary point of nonconvex problem in Appendix A-D.
	\end{itemize}

	We have made changes in Appendices A-C and A-D to address the concerns raised by the reviewer.

@@

	\vspace{1eM}	
	\item \reviewF{Even under the assumption that the inner loop SCA converges, there are doubts with respect to the convergence of the alternating optimization algorithm described by (54). The authors cite [27] to justify convergence, but it is not straightforward to claim that the algorithmic model considered in this manuscript is the same as in [27]. More specifically, let us consider the variable \eqn{x} (so it is consistent with the authors' notation in Appendix A-D). In the algorithmic model of [27], at iteration \eqn{t+1}, all elements of \eqn{\mbf{x}} are updated simultaneously, based on \eqn{\sol{t}}. But in the authors' model, the update of \eqn{\mbf{x}} is performed in two phases: in the first phase, only the elements of \eqn{\mbf{m}} and \eqn{\mbf{\gamma}} in \eqn{\mbf{x}} are updated based on \eqn{\sol{t}}. In the second phase, the remaining elements of \eqn{\mbf{x}} are updated, i.e. \eqn{\mbf{w}} and \eqn{\mbf{\gamma}}, based on both \eqn{\sol{t}} and the elements that have been updated in the first phase. This is not a trivial difference and thus the direct application of the conclusion from [27] in the current context cannot be taken for granted. Due to the open concerns after several revision rounds, it is recommended to reject the paper.}

	\vspace{1eM}
	\underline{\textbf{Response:}} We understand the reviewer's concern on using [R1] to our problem involving both \ac{SCA} and \ac{AO} updates. In each iteration, the proposed method solves only a subset of optimization variables by keeping others fixed, therefore, we cannot use [R1] directly as suggested by the reviewer. Even though we have revised our convergence proof based on a convergent subsequence without referring to [R1], nevertheless, we clarify our usage of [R1] in our previous manuscript for the convergence of iterates.

	\begin{itemize}
		\item We refer to [R2] for a similar usage of [R1] while discussing the convergence of \ac{AO} method used in designing tight frames by solving matrix nearness problem. In order to discuss the convergence of iterates generated by the \ac{AO} method, [R1] is used by referring \ac{AO} update as a composition of two sub-algorithms, wherein each sub-algorithm updates only a subset of optimization variables. It has been discussed briefly in [R2, Appendices I and II], and in particular for \ac{AO} algorithm in [R2, Appendix I-F].
		\item However, we apologize for the incomplete usage of [R1, Theorem 3.1] in our previous manuscript to claim the convergence of beamformer iterates. In [R1, Theorem. 3.1], it has been shown that if the strict monotonicity of the objective sequence is ensured and the iterates are bounded, then \textit{either the sequence of iterates converges or the accumulation points of \eqn{\{\sol{t}\}} is a continuum}.
		\item Therefore, our previous claim on the guaranteed convergence of iterates is not correct, as pointed out by the reviewer. 
		\item Similar approach of restricting the solution set with a proximal operator to ensure strict monotonicity of the objective sequence is discussed in [R1, Section 4] under restrictive mapping. Therefore, if we use the discussions in [R1], we can only claim that the sequence of iterates \eqn{\{\sol{t}\}} converges to a continuum of accumulation points, and every limit point is a stationary point.
	\end{itemize}

	We have revised Appendix A-D titled \textit{"Stationarity of Limit Points"} to discuss the convergence of the sequence of iterates. We have shown that every limit point of the sequence of iterates generated by the centralized algorithm is a stationary point.

	\vspace{1eM}
	\begin{itemize}		
		\item[R1.] R.R. Meyer, ``Sufficient Conditions for the Convergence of Monotonic Mathematical Programming Algorithms," \emph{Journal of Computer and System Sciences}, vol. 12, no. 1, pp. 108-121, 1976
		\item[R2.] J. Tropp, I. Dhillon, R. Heath, and T. Strohmer, ``Designing structured tight frames via an alternating projection method," \emph{IEEE Trans. Inform. Theory}, vol. 51, no. 1, pp. 188–209, Jan. 2005.
	\end{itemize}

\end{enumerate}

### 2015-11-20 Report/convergence_centralized.tex
with Antti reviews

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Objective function should be bounded below
\item[(b)] Feasible set should be compact
\item[(c)] Sequence of objective values should be strictly decreasing
\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
Note that condition (d) is required to ensure strict monotonicity of the objective sequence. Therefore, by using above conditions (a)-(c) along with \cite[Th. 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}. Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by the Algorithm \ref{algo-1} is a stationary point of original nonconvex problem formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
The feasible sets of the problems \eqref{eqn-6} and \eqref{eqn-mse-1} are bounded and closed, due to the total power constraint on transmit precoders \eqref{eqn-6.4}, therefore, the sets are compact.

The minimum value of the norm function in the objective is \me{\|x\|_q > -\infty}, therefore, it is bounded below. Additionally, the objective function is Lipschitz continuous and due to the fact that the feasible set is compact, objective function is bounded from above as well.

@@

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} to exploit the uniqueness of the minimizer at each iteration. However, we note that upon convergence \eqn{f} is equal to \eqn{\hat{f}}. Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.

@@

Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}. Since \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, 
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}
\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}. Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges. Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in every \ac{SCA} and \ac{AO} step.}

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector staking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

\review{Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop. A.3]{bertsekas1999nonlinear}. Similarly, in order to ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, let us prove the monotonicity of \eqn{\{\hat{f}(\ma^t)\}} by considering an instant \eqn{t}. Let \eqn{\mat{t}} and \eqn{\mat{t+1}} be the minimizers of \eqref{con-m} for the iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Then, by using \eqref{mod_obj} with the proximal term \eqn{\|\mat{} - \mat{t}\|^2} at \eqn{t}, we have
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t})
\end{equation}
where \eqn{\tau^t} is defined as \eqn{\tau_k^{(i)}} in \eqref{mod_obj}. Additionally, by using Appendix \ref{c-a}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by using \cite[Prop. A.3]{bertsekas1999nonlinear}. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.}

@@

@@

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
If follows immediately from \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr} that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can prove that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of the problem \eqref{con}.}

>>>>

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
\item[(a)] Uniqueness of the minimizer in each step
\item[(b)] Objective function should be bounded below
\item[(c)] Feasible set should be compact
\item[(d)] Sequence of objective values should be strictly decreasing
\end{itemize}
Note that condition (a) is required to ensure strict monotonicity of the objective sequence. Therefore, by using above conditions (a)-(d) along with \cite[Th. 3.14]{rudin1964principles}, we show the convergence objective sequence generated by Algorithm \ref{algo-1}. Then, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by the Algorithm \ref{algo-1} is a stationary point of original nonconvex problem formulations in \eqref{eqn-6} and \eqref{eqn-mse-1}}.

@@

@@

\subsection{Bounded Objective Function and Compact Feasible Set} \label{b_obj}
The feasible set of problems \eqref{eqn-6} and \eqref{eqn-mse-1} is bounded and closed due to the total power constraint on transmit precoders by \eqref{eqn-6.4} and \eqref{eqn-mse-1.4}, therefore, the feasible region is compact.

The minimum value of the norm function present in the objective is \me{\|\tilde{\mbf{v}}\|_q \geq 0} for all exponents used in \eqn{\ell_q} norm, therefore, it is bounded from below. Moreover, by the fact that the feasible set is compact, the objective function is Lipschitz continuous, and therefore bounded from above as well.

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} to exploit the uniqueness of the minimizer at each iteration. However, we note that upon convergence \eqn{f} is equal to \eqn{\hat{f}}. Therefore, the discussions are valid for the \ac{JSFRA} problems in \eqref{eqn-6} and \eqref{eqn-mse-1} by regularizing the objective functions \eqref{eqn-6.1} and \eqref{eqn-mse-1.1} as \eqref{mod_obj}.

@@

Finally, to prove the global convergence of the \reviewF{objective sequence}, we need to show that the \ac{AO} updates also produce a nonincreasing sequence of objectives, \textit{i.e.}, 
\iftoggle{single_column}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}{
\begin{equation}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}}
Let \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\mz}{\lpoint|\my}{i}} be the solution obtained by solving \eqref{con-m} iteratively until \ac{SCA} convergence in the \me{\ith{i}} \ac{AO} iteration for \eqn{\mx} and \eqn{\mz} with fixed \eqn{\my = \iter{\my}{\lpoint}{i-1}}. To find \me{\iter{\my}{0}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\lpoint}{i}} and optimize for \me{\my}. Since the constraint \eqref{con-dc-m} is linearized around \eqn{\iter{\mbf{z}}{\lpoint}{i}}, the fixed operating point is also included in the feasible set by following \eqref{con-sub-set} as \eqn{\{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\} \in \iter{\mc{Y}}{0}{i}}, therefore, we have
\begin{equation} \label{fixed_point}
f(\iter{\mx}{\lpoint}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}).
\end{equation}
\reviewF{Now, by using \eqref{con-dc-m}, we can ensure that \eqn{\iter{\mbf{z}}{\lpoint}{i} \in \{ \iter{\mc{X}}{\lpoint}{i} \cap \iter{\mc{Y}}{0}{i} \}} in each \ac{AO} update \eqn{i} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz}. Moreover, due to strong convexity of the objective function \eqref{mod_obj}, by following \eqref{strict_monotonicity}, we can show that \eqref{fixed_point} holds with strict inequality in each \ac{AO} update unless the overall objective sequence converges. Now, by combining \eqref{con-convergence}, \eqref{strict_monotonicity} and \eqref{fixed_point}, we can ensure strictly nonincreasing nature of the objective sequence \eqn{\{f(\mbf{z}^{(i)}_k)\}} in every \ac{SCA} and \ac{AO} step.}

\subsection{Stationarity of Limit Points} \label{c-b}
\reviewF{We discuss the convergence of the iterates generated by the iterative algorithm. In order to do that, let us use consider a single global indexing \eqn{t} to represent both \ac{SCA} step \eqn{k} and \ac{AO} index \eqn{i}. It corresponds to every \ac{AO} iterations and \ac{SCA} updates performed within each of the \ac{AO} step.
Using the unified index \eqn{t}, we denote iterate \eqn{\ma^{t}} as a vector stacking all optimization variables produced in every \ac{SCA} iteration \eqn{{k}} and \ac{AO} step \eqn{{i}}.

\review{Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop. A.3]{bertsekas1999nonlinear}. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.}

@@

\review{Before proceeding further, we ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}} by showing that \eqn{\{\hat{f}(\ma^t)\}} is monotonically decreasing in each step \eqn{t}. To do so, let us consider the minimizers \eqn{\mat{t}} and \eqn{\mat{t+1}} of problem \eqref{con-m} in iterations \eqn{{t-1}} and \eqn{{t}}, respectively. Then, by using \eqn{\mat{t}} in the proximal term of \eqref{mod_obj} as \eqn{\|\mat{} - \mat{t}\|^2}, the following inequality holds at every update step \eqn{{t}} as
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \|^2 \leq \hat{f}(\mat{t})
\end{equation}
where \eqn{\tau^t} is defined as \eqn{\tau_k^{(i)}} in \eqref{mod_obj} and \eqn{\|\mat{t+1} - \mat{t} \|^2 \geq 0}. Therefore, by using \eqref{mcity_origfunc} and Appendix \ref{b_obj}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be established by using \cite[Prop. A.3]{bertsekas1999nonlinear}.}

@@

Using \eqref{con-sub-set}, we have \eqn{\mc{X}_{k}^{(i)} \subset \mc{F}} and \eqn{\mc{Y}_{k}^{(i)} \subset \mc{F}}, therefore, \eqn{\bar{\ma}} is a feasible point for \eqref{con}. Moreover, the interiors of \eqn{\mc{X}_{k}^{(i)}} and \eqn{\mc{Y}_{k}^{(i)}} are non-empty, therefore, Slater's constraint qualification holds for \eqref{con-m}. Since \eqn{\bar{\ma}} is the solution for \eqref{con-m} as \eqn{k \to \infty,i \to \infty}, there exist Lagrange multipliers \eqn{\mu_i \geq 0} that  satisfies
\begin{equation} \label{kkt_mod_expr}
\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term in \eqref{mod_obj} \eqn{\|\ma^{t_{j+1}} - \ma^{t_j}\|^2 \to 0}  as \eqn{j \to \infty, \ma^{t_j} \to \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of a convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the continuity of function \eqn{g_o} and \eqref{con-relax}, equivalence between the gradient of \eqref{con-dc} and \eqref{con-dc-m} is obtained as \eqn{\ma^{t_j} \to \bar{\ma}}
\begin{equation} \label{rhs_equiv}
\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
If follows immediately from \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr} that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. Finally, by following \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can prove that every limit point of sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of the problem \eqref{con}.}

### 2015-11-20 Report/dual_approach.tex
with Antti reviews

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large enough to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of iterations, say, for \eqn{J_{\max}} only. In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.}

>>>>

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large enough to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of iterations, say, for \eqn{J_{\max}} only. In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be ensured, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. It follows from the fact that in each primal or \ac{ADMM} update, the global objective cannot be guaranteed to decrease monotonically.}

### 2015-11-20 Report/simulation_distributed.tex
with Antti reviews

Fig. \ref{fig-d-3.1} compares the performances of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \ac{PL} chosen uniformly between \me{[0,-3]} dB. The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other schemes due to the greedy nature of the objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}. A heuristic method is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when \me{Q_k - t_k < 0} to addresses the over-allocation. The heuristic approach oscillates near the converging point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}. The objective values are mentioned in the legend for all the schemes and the \me{\ell_1} norm is used for comparison.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-9-3}
	\vspace{-0.2in}
	\caption{Impact of varying \me{q} on the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace} and \me{Q_k = [9,16,14,16,9,13,11,12]} bits}
	\label{fig-d-3.1}
\end{figure}

>>>>

Fig. \ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \ac{PL} chosen uniformly between \me{[0,-3]} dB. The \me{\ell_1} norm \ac{JSFRA} scheme performs better over other \eqn{\ell_q} norms due to the greedy nature of the objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}. A heuristic method is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when \me{Q_k - t_k < 0} to addresses the over-allocation. The heuristic approach oscillates near the converging point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}. The objective values are mentioned in the legend for all the schemes and the \me{\ell_1} norm is used for comparison.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-9-3}
	\vspace{-0.2in}
	\caption{Impact of varying \me{q} on the total number of backlogged packets after each \ac{SCA} update for a system \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 5,2,8,4,1 \rbrace} and \me{Q_k = [9,16,14,16,9,13,11,12]} bits}
	\label{fig-d-3.1}
\end{figure}
